``{r setup, include=FALSE}
# set global chunk options
opts_chunk$set(cache=TRUE)
```
run_analysis,markdown version
====================================
This is the markdown version of the `run_analysis.R` script for conveniece

###Step 0: Read in data

The dataset is downloaded by running `downloadData.R`, which downloads and stores the data locally in the current directory's `UCI HAR Dataset` folder.

```{r downloadData, cache=TRUE}
if ( !file.exists("UCI HAR Dataset") )  downloadData()
```

We will be using `data.table`instead of `data.frame`s to speeds up processing

```{r load libraries}
library(data.table)
library(reshape2)
```

```{r readData, cache=TRUE}
path <- file.path("./", "UCI HAR Dataset")
list.files(path, recursive = TRUE)

### read the subject files (`subject IDs`):
DT.subject.ID.Train <- fread(file.path(path, "train", "subject_train.txt"))
DT.subject.ID.Test <- fread(file.path(path, "test", "subject_test.txt"))

### create datatable from data files
df <- read.table(file.path(path, "train", "X_train.txt"))
DT.train <- data.table(df)
df <- read.table(file.path(path, "test", "X_test.txt"))   
DT.test <- data.table(df)
```
 
 ### Step 1: Merge the training and the test sets to create one data set.
```{r mergeData}

# subject IDs:
DT.All.subject.IDs <- rbind(DT.subject.ID.Train, DT.subject.ID.Test)
setnames(DT.All.subject.IDs, "V1", "subject")  #10, 299 total subjects

# labels: 
DT.All.labels <- rbind(DT.label.Train, DT.label.Test)
setnames(DT.All.labels, "V1", "activity.label")

# the `train` and `test` dataset:
DT.Train.and.Test <- rbind(DT.train , DT.test)

# Merging columns of labels:
DT.All <- cbind(DT.All.subject.IDs, DT.Train.and.Test)
DT.All <- cbind(DT.All, DT.All.labels)
